---
title: "Fundamentals of Computing and Data Display"
subtitle: Exercise
output:
  html_document:
    df_print: paged
---

## Setup

```{r}
library(RSocrata)
library(jsonlite)
library(tidyverse)
library(lubridate) 
```

## Data

In this notebook, we use crime data from the City of Cincinnati, January to April 2020. "Incidents are the records, of reported crimes, collated by an agency for management."

Source: https://dev.socrata.com/foundry/data.cincinnati-oh.gov/k59e-2pvf

```{r}
cincinnati <- read.socrata("https://data.cincinnati-oh.gov/resource/k59e-2pvf.json?$where=date_reported between '2020-01-01' and '2020-04-15'")

```

Data prep and overview.

```{r}
cincinnati$datetime <- as_datetime(cincinnati$date_reported)
cincinnati$date <- date(cincinnati$datetime)
cincinnati$hourofday <- hour(cincinnati$datetime)
names(cincinnati)
View(cincinnati)
```

## ggplot

The first task is to create a basic barplot for `offense` to get an idea of the prevalence of different types of crimes. It might make sense to flip the graph to make the labels more readable.

```{r}

```

Calculate the total number of criminal offenses grouped by `dst` and `offense`. Try to create boxplots for each `offense` that visualize the distribution of the total number of crimes. Again, flip the graph to make the labels more readable.

```{r}

```

Create a plot that visualizes the total number of criminal offenses over `hourofday`. Draw separate lines for each `dayofweek` (note https://ggplot2.tidyverse.org/reference/aes_group_order.html).

```{r}

```

Focus only on the two most common types of crimes. Visualize the total number of offenses for these types of crimes over `hourofday`, separate for each `dayofweek`. Stated differently -- find a good way to visualize crime trends with an additional grouping variable.

```{r}

```

Again, plot the total number of crimes over `hourofday`, but this time we want to have a separate plot for each `offense` (`THEFT` and `CRIMINAL DAMAGING/ENDANGERING`) and `dayofweek` combination. Add an additional layer of your choice to each individual plot that uses another `geom` (with the same data).

```{r}

```

Try to create a heatmap (not a geographic map) that visualizes the total number of crimes per `hourofday` and `dayofweek`. Check the `ggplot()` documentation to find out which `geom_function` can be used for this task.

```{r}

```

Extend your heatmap by adding more information. This could e.g. be a `geom_text` layer that prints the total number of crimes in each cell of the heatmap. 

```{r}

```

Building on the previous examples, create two separate heatmaps for `THEFT` and `CRIMINAL DAMAGING/ENDANGERING` via faceting.

```{r}

```

Finally, build a plot that visualizes the crime trend/ the total number of crime offenses over the whole time range of our data. Add any layer, aesthetic or facet that you find useful. 

```{r}

```
